---
title: "NB"
author: "Hengxin Wu"
date: "11/22/2021"
output: html_document
---

```{r}
library(tm)
#install.packages("tm")
library(stringr)
library(wordcloud)
# ONCE: install.packages("Snowball")
## NOTE Snowball is not yet available for R v 3.5.x
## So I cannot use it  - yet...
##library("Snowball")
##set working directory
## ONCE: install.packages("slam")
library(slam)
library(quanteda)
## ONCE: install.packages("quanteda")
## Note - this includes SnowballC
library(SnowballC)
library(arules)
##ONCE: install.packages('proxy')
library(proxy)
library(cluster)
library(stringi)
library(proxy)
library(Matrix)
library(tidytext) # convert DTM to DF
library(plyr) ## for adply
library(ggplot2)
library(factoextra) # for fviz
library(mclust) # for Mclust EM clustering

library(naivebayes)
#Loading required packages
#install.packages('tidyverse')
library(tidyverse)
#install.packages('ggplot2')
library(ggplot2)
#install.packages('caret')
library(caret)
#install.packages('caretEnsemble')
library(caretEnsemble)
#install.packages('psych')
library(psych)
#install.packages('Amelia')
library(Amelia)
#install.packages('mice')
library(mice)
#install.packages('GGally')
library(GGally)
library(e1071)
library(ztable)
library(naivebayes)
library(tidyverse)
library(e1071)
library(caret)
library(ztable)
library(magrittr)
library(ggplot2)
library(cvms)
```

```{r}
setwd("/Users/hengxinwu/Desktop/DS Homework/501 Portfolio/NB and SVM/R")
```

```{r}
data1 <- read.csv("/Users/hengxinwu/Desktop/DS Homework/501 Portfolio/NB and SVM/R/NB.csv")
str(data1)
```

```{r}
data1$Threatened.Species..Vertebrates..number. <- as.numeric(data1$Threatened.Species..Vertebrates..number.)
data1$Income <- as.factor(data1$Income)
data1$Development <- as.factor(data1$Development)
str(data1)
```

```{r}
set.seed(1234)
size <- as.integer(nrow(data1)/4)
sample1 <- sample(nrow(data1), size, replace = TRUE)
testdata <- data1[sample1,]
traindata <- data1[-sample1,]
nrow(testdata)
nrow(traindata)
```

```{r}
testlabels <- testdata$Development
trainlabels <- traindata$Development
```

```{r}
newtestdata <- testdata[,-which(names(testdata)%in%c("Development"))]
head(newtestdata)
```

```{r}
newtraindata <- traindata[,-which(names(traindata)%in%c("Development"))]
head(newtraindata)
```

```{r}
nrow(newtestdata)
ncol(newtestdata)
nrow(newtraindata)
ncol(newtraindata)
```


```{r}
Accuracy=c()
Value_range<-seq(0.01, 10, 0.1)
for(laplace in Value_range){
  model<-naiveBayes(Development~.,data=traindata,laplace=laplace)
  prediction<-predict(model,newtestdata)
  Accuracy<-c(Accuracy,sum(prediction==testlabels)/nrow(testdata))
}
plot(Value_range,Accuracy,'l',xlab='Laplace Value')
```

```{r}
NB <- naiveBayes(newtraindata, trainlabels, laplace = 3.91)
NB_Pred <- predict(NB, newtestdata)
cm <- table(NB_Pred, testlabels)
```

```{r}
confusionMatrix(cm)
```

```{r}
heatmap(cm)
```

```{r}
NB
```

# According yo the graph, we can see that all of these variables are significant to the prediction, because when we see the condition probability for each variable, there us a significant difference between developed economies and developing economies by region #

# Accordig to the confusion matrix, out of 6 Developing economies by region, 6 Developing economics by region are successfullu classified as Developing economics by region, and 1 is classified as Developed economies. 6 Developed economies are correctly classified as the Developed economies. The Naive Bayes model shows a very high accuracy whcoih is 0.9167. #

```{r}
barplot(NB$apriori/sum(NB$apriori),main='Apriori Probabilities')
```







