---
title: "Decision Tree"
author: "Hengxin Wu"
date: "11/10/2021"
output: html_document
---

# Import Package
```{r}
library(rpart)   ## FOR Decision Trees
library(rattle)  ## FOR Decision Tree Vis
library(rpart.plot)
library(RColorBrewer)
library(Cairo)
library(network)
library(ggplot2)
##If you install from the source....
#Sys.setenv(NOAWT=TRUE)
## ONCE: install.packages("wordcloud")
library(wordcloud)
## ONCE: install.packages("tm")

library(slam)
library(quanteda)
## ONCE: install.packages("quanteda")
## Note - this includes SnowballC
#library(SnowballC)

library(proxy)
## ONCE: if needed:  install.packages("stringr")
library(stringr)
## ONCE: install.packages("textmineR")
library(textmineR)
library(igraph)
library(caret)
```

# Import data #
```{r}
setwd('/Users/hengxinwu/Desktop/DS Homework/501 Portfolio/Decision Trees/R')
data1 <- read.csv('DT.csv')
head(data1)
```

# check the data type #
```{r}
str(data1)
data1$Development <- as.factor(data1$Development)
data1$Income <- as.factor(data1$Income)
```

```{r}
str(data1)
```

```{r}
library(ggplot2)
## Define the function on any dataframe input x
GoPlot <- function(x) {
  
  G <-ggplot(data=data1, aes(.data[[x]], y="") ) +
  geom_bar(stat="identity", aes(fill =.data[[x]])) 
  
  return(G)
}
## Use the function in lappy
lapply(names(data1), function(x) GoPlot(x))
```

# Split into TRAIN and TEST data #
```{r}
(DataSize=nrow(data1)) ## how many rows?
(TrainingSet_Size<-floor(DataSize*(3/4))) ## Size for training set
(TestSet_Size <- DataSize - TrainingSet_Size) ## Size for testing set
```

```{r}
set.seed(1234)
## This is the sample of row numbers
(MyTrainSample <- sample(nrow(data1), TrainingSet_Size,replace=FALSE))
## Use the sample of row numbers to grab those rows only from
## the dataframe....
(MyTrainingSET <- data1[MyTrainSample,])
table(MyTrainingSET$Development)
## Use the NOT those row numbers (called -) to get the
## other row numbers not in the training to use to create
## the test set.
## Training and Testing datasets MUST be disjoint. Why?
(MyTestSET <- data1[-MyTrainSample,])
table(MyTestSET$Development)
##Make sure your Training and Testing datasets are BALANCED
```

# Remove label from the Test datatset #
```{r}
(TestKnownLabels <- MyTestSET$Development)
(MyTestSET <- MyTestSET[ , -which(names(MyTestSET) %in% c("Development"))])
```

# Create a Decision Tree #
```{r}
DT1 <- rpart(MyTrainingSET$Development ~ ., data = MyTrainingSET, method="class")
```

# VIS #
```{r}
fancyRpartPlot(DT1)
```

# feature importance #
```{r}
importance1 <- DT1$variable.importance
opar <- par(no.readonly = TRUE)
par(pin = c(3, 3))
barplot(importance1, horiz = TRUE, las = 1)
par(opar)
```

# Make a prediction and create a confusion matrix #
```{r}
(DT_Prediction1 = predict(DT1, MyTestSET, type="class"))
## Confusion Matrix
table(DT_Prediction1,TestKnownLabels) ## one way to make a confu mat
heatmap(table(DT_Prediction1,TestKnownLabels))
```

# Second decision tree #
```{r}
DT2 <- rpart(MyTrainingSET$Development ~ ., data = MyTrainingSET, cp=0, method="class", minsplit=3)
fancyRpartPlot(DT2)
```

# feature importance #
```{r}
importance2 <- DT2$variable.importance
opar <- par(no.readonly = TRUE)
par(pin = c(3, 3))
barplot(importance2, horiz = TRUE, las = 1)
par(opar)
```

# Make a prediction and create a confusion matrix #
```{r}
(DT_Prediction2 = predict(DT2, MyTestSET, type="class"))
## Confusion Matrix
table(DT_Prediction2,TestKnownLabels) ## one way to make a confu mat
heatmap(table(DT_Prediction2,TestKnownLabels))
```

# Third decision tree #
```{r}
DT3 <- rpart(MyTrainingSET$Development ~ Forest.cover.percentage + Emissions + Income, data = MyTrainingSET, cp=0, method="class", minsplit=3)
fancyRpartPlot(DT3)
```

# feature importance #
```{r}
importance3 <- DT3$variable.importance
opar <- par(no.readonly = TRUE)
par(pin = c(3, 3))
barplot(importance3, horiz = TRUE, las = 1)
par(opar)
```

# Make a prediction and create a confusion matrix #
```{r}
(DT_Prediction3 = predict(DT3, MyTestSET, type="class"))
## Confusion Matrix
table(DT_Prediction3,TestKnownLabels) ## one way to make a confu mat
heatmap(table(DT_Prediction3,TestKnownLabels))
```





